An analysis of Lenin's work: Revolution, war, and fruta

### 2013-12-21 paper/distance.tex
Add separate paper for distance function.

\begin{article}
\begin{abstract}
In order to discover how much related were Lenin Works to Russian History in nearly 20th century, we use the information value concept to extract the most important words from them. Therefore, we find out how far are them from certain concepts such as
war, revolution, theory, etc. We expected this concepts to be nearer and farther to concepts 
treated in Lenin's works depending on the events ranging from 1900 to 1924.
\end{abstract}

@@

Having these value, we can pull the most representative words out of a text by selecting those of greater information value.

\section{Method}
\subsection{Text Corpus}
We gathered Lenin's work from the "Marxists Internet Archive". This proved to be a difficult task as the works were not in a common HTML format. The tool we used to do this is Scrapy, a very comprehensive Python crawling framework.

In order to reduce noise in the corpus, we filtered all the letters and works that were comparatively little. Our information value theory doesn't work very well with texts with little repetition of words, so we decided to remove texts with less than 2000 words.

\begin{figure}
\centerline{\includegraphics[width=.4\textwidth]{figures/tokens_per_year.eps}}
\caption{Number of works per year}\label{afoto}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=.4\textwidth]{figures/hist_tokens_small_works.eps}}
\caption{Distribution of works with respect to size (small works)}\label{afoto}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=.4\textwidth]{figures/hist_tokens_big_works.eps}}
\caption{Distribution of works with respect to size (big works)}\label{afoto}
\end{figure}

>>>>

\begin{article}
\begin{abstract}
In order to discover how much related were Lenin Works to Russian History in nearly 20th century, we use the information value concept to extract the most important words from them. Therefore, we find out how far are them from certain words such as
war, revolution, theory, etc giving a Wordnet-based similarity function. 
\end{abstract}

@@

Having these value, we can pull the most representative words out of a text by selecting those of greater information value. Now our question arises: how distant is a word from a text? We use here the notion of distance between a point and a set defined as:

\begin{equation}
  d(a, S) = min_{x \in S} d(a, x) 
\end{equation}

being $S$ the set of most representative words. Hence, we are ``projecting'' a text into the set of their top words.

\section{Method}
\subsection{Text Corpus}
We selected some starred works from Lenin from the "Marxists Internet Archive". Those works are very different in topic, some of them being strictly phylosophical essays (such as ``Materialism and Empiriocriticism'') and other being more political, such as ``State and Revolution'', and finally an economy essay called ``Imperialism, the highest stage of capitalism''

\begin{itemize}
  \item What is to be done(1901)
  \item Materialism and Empiriocriticism (1908)
  \item Imperialism, the highest stage of capitalism (1916)
  \item State and Revolution (1917)
\end{itemize}
